\papertitle

### 2021-03-08 source_separation/paper/paper.tex
Add names and affiliations

% Authors
% Please note that submissions are NOT anonymous, therefore 
% authors' names have to be VISIBLE in your manuscript. 
% Authors are entered as an ordered list, each one can be linked to multiple affiliations using the correct index.
% Available tags for authors are: \firstname \middlename \lastname \generation \originalname \email \orcid
% Available tags for affiliations are: \unit \department \institution \streetaddress \city \state \postcode \country \type
% type can take as value: University, Company, Music, Independent, Other
%
% \author[]{\mbox{\firstname{}\middlename{}\lastname{}\originalname{}\generation{}\email{}\orcid{}}}
% mbox force an author not to be split over multiple lines
\author[1]{\mbox{\firstname{Luke}\lastname{Dzwonczyk}\email{dz.luke@berkeley.edu}}}
\author[1, 2]{\mbox{\firstname{L\'eo}\lastname{Chedin}}}
\author[1]{\mbox{\firstname{Alejandro}\lastname{Saldarriaga-Fuertes}}}
\author[1]{\mbox{\firstname{Max}\lastname{Sherr}}}
\author[1]{\mbox{\firstname{H\'el\`ene-Camille}\lastname{Crayencour}}}
\author[1]{\mbox{\firstname{Carmine-Emanuele}\lastname{Cella}}}

%%Affiliations
\affil[1]{\department{Center for New Music and Audio Technologies}\institution{University of California, Berkeley}\city{Berkeley}\state{California}\country{USA}\affiliationtype{University}}
\affil[2]{\department{ENS}\institution{}\city{Paris}\state{}\country{France}\affiliationtype{University}}

>>>>

% Authors
% Please note that submissions are NOT anonymous, therefore 
% authors' names have to be VISIBLE in your manuscript. 
% Authors are entered as an ordered list, each one can be linked to multiple affiliations using the correct index.
% Available tags for authors are: \firstname \middlename \lastname \generation \originalname \email \orcid
% Available tags for affiliations are: \unit \department \institution \streetaddress \city \state \postcode \country \type
% type can take as value: University, Company, Music, Independent, Other
%
% \author[]{\mbox{\firstname{}\middlename{}\lastname{}\originalname{}\generation{}\email{}\orcid{}}}
% mbox force an author not to be split over multiple lines
\author[1]{\mbox{\firstname{Luke}\lastname{Dzwonczyk}\email{dz.luke@berkeley.edu}}}
\author[1, 2, 3]{\mbox{\firstname{L\'eo}\lastname{Chedin}}}
\author[1]{\mbox{\firstname{Alejandro}\lastname{Saldarriaga-Fuertes}}}
\author[1]{\mbox{\firstname{Max}\lastname{Sherr}}}
\author[3]{\mbox{\firstname{H\'el\`ene-Camille}\lastname{Crayencour}}}
\author[1]{\mbox{\firstname{Carmine-Emanuele}\lastname{Cella}}}

%%Affiliations
\affil[1]{\department{Center for New Music and Audio Technologies}\institution{University of California, Berkeley}\city{Berkeley}\state{California}\country{USA}\affiliationtype{University}}
\affil[2]{\department{\'Ecole Normale Sup\'erieure Paris-Saclay}\institution{Universi\'e Paris-Saclay}\city{Paris}\state{}\country{France}\affiliationtype{University}}
\affil[3]{\department{Laboratoire des Signaux et Syst\`emes}\institution{Centrale Supélec, CNRS, Université Paris-Saclay}\city{Paris}\state{}\country{France}\affiliationtype{University}}
